Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-11-16 fib2.tex
update

A modular functor $\F$ associates to every
surface $M$ a finite dimensional complex
vector space $\F(M)$, called the \emph{fusion space} of $M$.
A map of surfaces $f:M\to N$ will be understood to be
a topological homeomorphism that preserves boundary
labels and orientation, and
the modular functor assocates such an $f$ to a
unitary transformation $\F(f) : \F(M)\to\F(N).$
Functoriality requires that $\F$
respect composition of homeomorphisms.

@@

{\bf Axiom II.}
The disjoint union of two surfaces $M$ and $N$ 
is assocated with
the tensor product of fusion spaces:
$$
    \F(M\amalg N) \cong \F(M)\otimes \F(N).
$$
This is natural from the point of view of quantum
physics, where the Hilbert space of two disjoint
systems is the tensor product of the space for
each system.

@@

@@

This is not at all the case in general;
for non-Abelian theories there can be extra
degrees of freedom associated with these
observables. For example, in
a system supporting Fibonacci anyons,
we can have two Fibonacci anyons with total
charge either vacuum or Fibonacci:
\begin{center}
\includegraphics[]{pic-fusion.pdf}
\end{center}
so the state space of two fibonacci anyons
is $2$-dimensional.
Such a space assocated with observing total charge
of multiple anyons is called the \emph{fusion} space
of those charges.

@@

The importance of this isomorphism: the simulation
algorithm calculates outcomes of observations. This
boils down to a change of basis, to one that includes
the required observable.
$F$-moves allow us to re-assocate observables along
a curve diagram. The mapping class group acts
transitively on curve diagrams (\emph{why??}).

>>>>

A modular functor $\F$ associates to every
surface $M$ a finite dimensional complex
vector space $\F(M)$, called the \emph{fusion space} of $M$.
A map of surfaces $f:M\to N$ will be understood to be
a topological homeomorphism that preserves boundary
labels, orientation, and distinguished points.
The modular functor associates such an $f$ to a
unitary transformation $\F(f) : \F(M)\to\F(N)$
that only depends on the isotopy class of $f.$
Functoriality requires that $\F$
respect composition of homeomorphisms.

@@

{\bf Axiom II.}
The disjoint union of two surfaces $M$ and $N$ 
is associated with
the tensor product of fusion spaces:
$$
    \F(M\amalg N) \cong \F(M)\otimes \F(N).
$$
This is natural from the point of view of quantum
physics, where the Hilbert space of two disjoint
systems is the tensor product of the space for
each system.

@@

Any oriented simple closed path contained in the interior of $M$ we will
call an \emph{observable}.
Such a path that encloses two boundary components 
we call a \emph{2-observable}.
A function $c:[0,1]\to M$ such that $c(0)\in \partial M$ and $c(1)\in \partial M$
are two separate components of the boundary we call a \emph{2-curve.}
The following important fact will be used extensively
in the combinatorial formulation of a modular functor below:
up to isotopy (not preserving $\partial M$),
there is a (natural) bijection between
$2$-observables and $2$-curves.

@@

This is not at all the case in general;
for non-Abelian theories there can be extra
degrees of freedom associated with these
observables. For example, in
a system supporting Fibonacci anyons,
we can have two Fibonacci anyons with total
charge either vacuum or Fibonacci:
\begin{center}
\includegraphics[]{pic-fusion.pdf}
\end{center}
so the state space of two fibonacci anyons
is $2$-dimensional.
Such a space associated with observing total charge
of multiple anyons is called the \emph{fusion} space
of those charges.

@@

The importance of this isomorphism: the simulation
algorithm calculates outcomes of observations. This
boils down to a change of basis, to one that includes
the required observable.
$F$-moves allow us to re-associate observables along
a curve diagram. The mapping class group acts
transitively on curve diagrams (\emph{why??}).
